---
title: "Linear Regression"
output: html_notebook
---

In the `.Rmd`-file, you can execute chunks by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

Suggested Experiments:

- Change the standard deviation of the noise and observe the effect this has on correlation,
- Compare the scaled and unscaled version of the data and observe which statistics changes and which do remain unchanged.

Load libraries.

```{r}
library(tidyverse)
library(moderndive)
```

Parameters of this notebook. Modify to run your own experiments.

```{r}
m <- 1 # slope of the linear model
b <- 2 # intercept of the linear model
n <- 30 # sample size
scale_x <- 2 # rescale x for comparison
scale_y <- 3 # rescale y for comparison
```

Create random data. The noise on y is sampled from a normal distribution.

```{r}
x <-  runif(30, 0, 10) # choose 30 random points on x between 0 and 10
noise <- rnorm(30, mean=0, sd=sd_y) # create some noise on y
y <- m*x + b + noise # compute y coordinates
pairs <- tibble(x,y) # make a table with all (x,y)
```

Glimpse at the data.

```{r}
print(pairs) 
```

Plot data and regression line.

```{r}
pairs %>%
  ggplot(aes(x,y)) +
    geom_point() +
    geom_smooth(formula = y ~ x, method = "lm", se=FALSE) + # "lm" computes a linear model (regression) +
    labs (title = "unscaled data")

```

Computer printout of regression.

```{r}
score_model <- lm(y ~ x, data = pairs) # compute the regression (lm for linear model)
get_regression_table(score_model) # output to the console
```

Get the Correlation.

```{r}
get_correlation(formula = y ~ x, data = pairs) # output to the console
```

Create rescaled data for comparison

```{r}
x <- scale_x*x # scale x
y <- scale_y*y # scale y
pairs_scaled <- tibble(x,y) # make table
```

Plot scaled data and regression line.

```{r}
pairs_scaled %>%
  ggplot(aes(x,y)) +
    geom_point() +
    geom_smooth(formula = y ~ x, method = "lm", se=FALSE) + # "lm" computes a linear model (regression) +
    labs (title = "scaled data")

```

Computer printout of regression for scaled data.

```{r}
score_model <- lm(y ~ x, data = pairs_scaled) # compute the regression (lm for linear model)
get_regression_table(score_model) # output to the console
```

Get the Correlation.

```{r}
get_correlation(formula = y ~ x, data = pairs_scaled) # output to the console
```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

